\section{Experimental Setup}
\label{sec:setup}

\subsection{Data: Wikidata-Derived Knowledge Graphs}

Three independent domain pairs were constructed from Wikidata SPARQL queries
with semi-manual bridge entity selection (Threat~T2.1; Section~\ref{sec:threats}).

\begin{description}[leftmargin=0pt]
\item[Subset~A --- Cancer Signaling / Metabolic Chemistry]
Bio KG: 293 nodes, 233 edges (cancer signaling genes, proteins, metabolites;
key entities: VHL, HIF1A, LDHA, NADH, mTOR, EGFR, KRAS).
Chem KG: 243 nodes, 191 edges (metabolic reactions and cofactors).
Aligned bridge pairs: 7 (NADH, NAD$^+$, ATP, ADP, Glucose, Pyruvate, Lactate).

\item[Subset~B --- Immunology / Natural Products]
Bio KG: 178 nodes, 122 edges (immune signaling, cytokines, receptors).
Chem KG: 110 nodes, 90 edges (natural products chemistry).
Aligned bridge pairs: 5 (eicosanoid metabolites: AA, PGE$_2$, LTB$_4$, PGI$_2$, TXA$_2$).

\item[Subset~C --- Neuroscience / Neuro-pharmacology]
Bio KG: 151 nodes, 128 edges (neurotransmitter synthesis, signaling).
Chem KG: 86 nodes, 78 edges (neuro-pharmacology, drug-receptor interactions).
Aligned bridge pairs: 9 (Dopamine, Serotonin, GABA, Norepinephrine + additional).
\end{description}

All experiments are fully deterministic (\texttt{random.seed=42}; no external API calls).

\subsection{Pipeline Conditions}

\begin{center}
\begin{tabular}{lll}
\toprule
Condition & Operators & Description \\
\midrule
P1 (single-op baseline) & compose only        & C1 condition; no alignment \\
P4 (multi-op)           & align+union+compose+difference+evaluate & C2; full pipeline \\
P4+filter               & P4 with drift filter & Run~012+ (Section~\ref{sec:filter}) \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Evaluation Metrics}

\begin{itemize}[noitemsep]
  \item \textbf{unique\_to\_alignment}: cross-domain candidate pairs reachable
    only via aligned bridge nodes (zero in P1)
  \item \textbf{deep CD count}: candidates with path length $\geq 3$ and
    cross-domain subject/object
  \item \textbf{drift rate by depth}: fraction of candidates at each depth
    containing at least one blocked relation
  \item \textbf{promising rate}: fraction of deep CD candidates labelled
    \textit{promising} in qualitative review (Run~011; Subset~A only)
  \item \textbf{top-20 depth composition}: depth distribution of top-20 scored candidates
\end{itemize}

\subsection{Run Progression}
\label{sec:runs}

Thirteen runs span four phases: synthetic KG validation (Runs~001--006),
first real-data test (Run~007), scale-up and operator development
(Runs~008--012), and reproducibility testing (Run~013).
Table~\ref{tab:run_summary} summarises the key results at each phase.

\begin{table}[h]
\caption{%
  \textbf{Run progression summary (Runs 001--013).}
  Phase 1--2: synthetic KG; Phase 3--4: Wikidata-derived KGs.
  H1''/H3''/H4 verdicts reflect final hypothesis formulations (see text).
}
\label{tab:run_summary}
\small
\begin{tabularx}{\linewidth}{lcllX}
\toprule
Run & Phase & Scale & Key finding & Verdict \\
\midrule
001--006 & 1--2 & 57n (synth) & Operator validation, rubric calibration & H1/H3/H4 PASS (synthetic) \\
007      & 3    & 57n (real)   & H1'' cond.\ PASS; 4 unique pairs via alignment & H1'' PASS (cond.) \\
008      & 3    & 57n (real)   & H3'' FAIL: 57 nodes structurally incapable of 3-hop CD & H3'' FAIL (scale) \\
009      & 4    & 536n (real)  & H3'' PASS (20 deep CD); H4 FAIL (old rubric) & H1'',H3'' PASS; H4 FAIL \\
010      & 4    & 536n         & H4 PASS: revised traceability; 309 deep promoted & H4 PASS \\
011      & 4    & 536n         & Qualitative review: 25\% drift, 15\% promising & Manual labels \\
012      & 4    & 536n         & Drift filter: 0\% drift, 100\% promising; 3 survivors & Filter derived \\
013      & 4    & 288--536n    & Reproducibility 3/3 subsets SUCCESS & H1'',H3'' confirmed \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Hypothesis Definitions}

\begin{description}[leftmargin=0pt]
\item[H1'']
The multi-operator pipeline produces a non-zero number of
\textit{unique\_to\_alignment} cross-domain candidate pairs, demonstrating that
alignment-dependent paths exist that compose cannot reach without bridge alignment.

\item[H2]
The pipeline output is noise-robust under random edge deletion.
\textit{(Validated on synthetic KG only; not retested on real data.)}

\item[H3'']
On a real KG of sufficient scale ($\geq$288 nodes), the pipeline generates
$\geq$1 deep ($\geq$3-hop) cross-domain candidate that passes the drift filter
and is labelled promising (or inferred promising via filter passage).

\item[H4]
The revised quality-aware traceability scorer ranks deep cross-domain candidates
higher relative to the naive depth-penalty scorer.

\end{description}

Final hypothesis verdicts are reported in Table~\ref{tab:hypothesis_status}.
