\section{Discussion}
\label{sec:discussion}

\subsection{Relation Semantic Insufficiency as a Unified Root Cause}

Run~014's relation semantics audit revealed that all five reviewed candidates carry
at least one relation edge where the KG's class-level encoding is insufficient to
validate a substrate-specific chemical or biological claim.
This finding unifies previously separate observations---B-1/B-2's directionality
problem, C-1's chemistry validity failure, and C-2's compartmentalisation risk---under
a single root cause:

\medskip
\noindent\textbf{Root cause}: The KG encodes relation types at the \textit{class level}
rather than the \textit{instance level}.
A relation of type \texttt{produces} between a reaction class and a functional group
class (e.g., $r$\_Methylation $\to$ $fg$\_Piperidine) asserts that the reaction
\textit{type} can produce compounds bearing the functional group in general, but does
not validate whether the specific substrate in the path actually undergoes this
transformation.
Similarly, a relation \texttt{is\_substrate\_of} between a metabolite and an enzyme
encodes shared-enzyme membership, not substrate-specific causal transmission.

\medskip
This is not a failure of the drift filter---the filter correctly identifies structural
relation categories.
It is a limitation of the KG's underlying schema: without substrate-specificity
metadata on \texttt{produces} edges, and without compartment annotations on nodes,
the pipeline cannot distinguish mechanistically valid paths from structurally valid
but biologically incorrect ones.
Table~\ref{tab:relation_semantics} summarises the five semantic categories
and their inferential properties.

\input{tables/table3_relation_semantics}

\subsection{The Alignment Operator as the Necessary Structural Primitive}

The align operator's mechanism---collapsing bridge entities to create a shared node
that BFS can traverse---is the necessary structural primitive for cross-domain discovery.
Without it, the composed graph has no edges crossing the domain boundary,
and compose cannot generate cross-domain candidates regardless of graph size.

This is a structural necessity (Claim~1), not a tuning choice.
The operator is analogous to Swanson's ABC model but formalised as a graph-algebraic
step: the bridge entity $B$ is the aligned node that connects $A$ (a bio entity)
to $C$ (a chem entity) via a path that could not exist in either domain alone.

\subsection{Quality Filtering: Generalisation Evidence and Residual Precision Gap}

The filter's generalisation across three independent domain pairs (Run~013) is
the strongest evidence against post-hoc overfitting.
A filter derived from 20 labeled candidates in one domain pair
(cancer signaling / metabolic chemistry) achieves identical qualitative outcomes
in two entirely different chemical systems (eicosanoid / natural products;
neurotransmitter / neuro-pharmacology) without parameter adjustment.

This suggests the four excluded relation types
(\texttt{contains}, \texttt{is\_product\_of}, \texttt{is\_reverse\_of},
\texttt{is\_isomer\_of}) represent a principled domain-general category:
structural-chemical description relations that are true but non-mechanistic.
The category appears stable across bio-chem domain pairs.

However, C-1 exposes a residual precision gap: the filter cannot distinguish
substrate-specific \texttt{produces} (bio enzyme $\to$ specific metabolite; safe)
from class-level \texttt{produces} (reaction class $\to$ functional group class; risky).
Both receive the same strong-relation credit.
Future filter versions should add a \texttt{produces\_class} flag to distinguish
these patterns, and should flag paths containing \texttt{is\_precursor\_of}
or \texttt{is\_substrate\_of} as carrying DN-category semantics.

\subsection{Bridge Dispersion: Design Implication for KG Construction}

The bridge dispersion finding (Claim~3) has a direct actionable implication for
knowledge graph curation targeting cross-domain discovery:
\textit{prefer bridge entities that are metabolic hubs or signaling intermediates
with many known interactors in both domains} over simply increasing the number
of bridge pairs.

Subset~B's five eicosanoids yield 8$\times$ more candidates per bridge than
Subset~A's NADH because each eicosanoid connects to multiple downstream synthesis
enzymes (bio) and natural product structural families (chem).
This amplification effect is non-linear: a metabolically diverse bridge class
generates combinations that a hub-low bridge cannot, regardless of how many
low-diversity bridge pairs are added.

\subsection{Top-20 Dominance by 2-Hop Candidates}

In all subsets and all scoring configurations, the top-20 candidates are exclusively
2-hop paths (mean score 0.78 across subsets).
The H4 result (Run~010) shows that the revised scorer improves the relative ranking
of deep candidates (309 promoted vs.\ 209 demoted), but does not change top-20
composition.
This is a systematic limitation: the absolute scoring advantage of well-supported
2-hop chains exceeds the relative gain from the quality-aware traceability revision.

Deep cross-domain candidates---the scientifically more interesting outputs---require
either a depth-promotion bonus, a minimum-depth tier, or a separate ranked list to
surface in practical use.
This is an unsolved problem in the current pipeline.
